Tutorial_2a

### 2024-12-05 Tutorial_2a.Rmd
added a figure with 6 hypothetical pids

```{r load-pkg, results='hide'}
pkg <- c("cmdstanr", "standist", "tidyverse", "RColorBrewer", "patchwork", 
         "brms", "tidybayes", "bayesplot", "future", "parallel", "modelr")

@@

>>>>

```{r load-pkg, results='hide'}
pkg <- c("cmdstanr", "standist", "tidyverse", "RColorBrewer", "patchwork", 
         "brms", "tidybayes", "bayesplot", "future", "parallel", "modelr",
         "rstan")

@@

Fourth, six completely new hypothetical participants.

```{r epred-new-pid-6}
epreds_pid_new6 <- dat_M1i %>% 
  data_grid(timebin, prime, pid = 7:12) %>%
  add_epred_draws(model_M1i, 
                  re_formula = NULL, 
                  allow_new_levels=T,    
                  sample_new_levels = "gaussian") %>% 
  mutate(prime = factor(prime, 
                        levels=c(1,2,3),
                        labels=c("blank","congruent","incongruent"))) %>%
  ungroup()
```

```{r epred-new-pid-6-summary}
epreds_pid_new6 %>% 
  group_by(pid,timebin,prime) %>% 
  median_qi(.width=.95)
```

```{r epred-new-pid-6-plot}
 ggplot(epreds_pid_new6, aes(x=timebin, y=.epred, 
                       fill=prime, color=prime)) +
    stat_lineribbon(point_interval="median_qi",
                    .width=.95,
                    alpha = 0.5) +
    scale_fill_brewer(palette = "Dark2") +
    scale_color_brewer(palette = "Dark2") +
    scale_x_discrete(labels = str_c("(",(c(6:15)-1)*40,",",c(6:15)*40,"]"), breaks = 6:15) +
    theme(axis.text.x = element_text(angle=90)) +
    scale_y_continuous(limits=c(0,1)) +
    labs(y = "predicted hazard") +
    ggtitle("Six new hypothetical participants") +
    facet_wrap(~pid, ncol=3)
```

```{r save-epred-pid-new, eval=F}
ggsave("Tutorial_2_Bayesian/figures/M1i_pred_pid_new_6.png", width = 10, height = 8, dpi = 800)
```
